Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-18 paper/paper.tex
Complete another study in the related work section

Other interesting findings regarding the quality of a software project's tickets
are the ones elicited in the study of Bettenburg et. al \cite{bettenburg2008duplicate}. The authors examined
whether duplicate bug reports are actually harmful to a project or they add 
quality. They collected big amount of data from the Eclipse project and ran
various kind of textual and statistical analysis on the data to find answers.
They reached the conclusion that bug duplicates contain information that is not
present in the master reports. This additional data can be helpful for developers
and it can also aid automated triaging techniques.

@@

\subsection{Attachments}
\begin{figure}
  \begin{center}
  \includegraphics[scale=0.25]{images/attachments.png}
  \end{center}
  \caption{\label{attachments}Application flow of the Go tool.}
  \end{figure}

\subsection{Comments}
\begin{figure}
  \begin{center}
  \includegraphics[scale=0.25]{images/comment_complexity.png}
  \end{center}
  \caption{\label{comments}Application flow of the Go tool.}
  \end{figure}

\subsection{Summary and Description}
\begin{figure}
  \begin{center}
  \includegraphics[scale=0.25]{images/fields_complexity.png}
  \end{center}
  \caption{\label{fields}Application flow of the Go tool.}
  \end{figure}

\subsection{Grammar Correctness}
\begin{figure}
  \begin{center}
  \includegraphics[scale=0.25]{images/grammar_correctness.png}
  \end{center}
  \caption{\label{grammar}Application flow of the Go tool.}
  \end{figure}

\subsection{Sentiment Scores}
\begin{figure}
  \begin{center}
  \includegraphics[scale=0.25]{images/sentiment_analysis.png}
  \end{center}
  \caption{\label{sentiment}Application flow of the Go tool.}
  \end{figure}

\subsection{Steps to Reproduce}
\begin{figure}
  \begin{center}
  \includegraphics[scale=0.25]{images/steps_to_reproduce.png}
  \end{center}
  \caption{\label{steps}Application flow of the Go tool.}
  \end{figure}

\subsection{Stack Traces}
\begin{figure}
  \begin{center}
  \includegraphics[scale=0.25]{images/stack_traces.png}
  \end{center}
  \caption{\label{stack_traces}Application flow of the Go tool.}
  \end{figure}

>>>>

Software tickets can have duplicates, usually meaning that the most important fields, such 
as summary or description, describe the same feature request or bug report. Even though 
one might believe that they cannot bring any value to a software project, the work of 
Bettenburg et. al \cite{bettenburg2008duplicate} shows the contrary.
The authors collected large amounts of data from the Eclipse open source project and ran
various kind of textual and statistical analysis on the data to find answers.
After the results were computed, they concluded that usually bug duplicates contain 
information that is not present in the master report (i.e. the original report that was 
filed). Moreover, developers also specified that they have often found value in these 
duplicate bug reports and that they can even aid automated triaging techniques.

@@

\subsection{Attachments}

A Welch T Test was computed to test the difference between tickets with attachments and those 
without attachments. The analysis revealed significant difference with \emph{p} < 0.01 with an
average of \emph{X <change this>} for tickets with attachments and an average of \emph{Y <change this>}
for tickets without attachments.

\begin{figure}
  \begin{center}
  \includegraphics[scale=0.25]{images/attachments.png}
  \end{center}
  \caption{\label{attachments}Application flow of the Go tool.}
  \end{figure}

\subsection{Steps to Reproduce}

A Welch T Test was computed to test the difference between tickets with attachments and those 
without attachments. The analysis revealed significant difference with \emph{p} < 0.01 with an
average of \emph{X <change this>} for tickets with attachments and an average of \emph{Y <change this>}
for tickets without attachments.

\begin{figure}
  \begin{center}
  \includegraphics[scale=0.25]{images/steps_to_reproduce.png}
  \end{center}
  \caption{\label{steps}Application flow of the Go tool.}
  \end{figure}

\subsection{Stack Traces}

A Welch T Test was computed to test the difference between tickets with attachments and those 
without attachments. The analysis revealed significant difference with \emph{p} < 0.01 with an
average of \emph{X <change this>} for tickets with attachments and an average of \emph{Y <change this>}
for tickets without attachments.

\begin{figure}
  \begin{center}
  \includegraphics[scale=0.25]{images/stack_traces.png}
  \end{center}
  \caption{\label{stack_traces}Application flow of the Go tool.}
  \end{figure}

\subsection{Comments}

A correlational analysis revealed a weak positive/negative (one of them, depending on context) relationship
with \emph{r} = \dots, \emph{p} = \dots.

\begin{figure}
  \begin{center}
  \includegraphics[scale=0.25]{images/comment_complexity.png}
  \end{center}
  \caption{\label{comments}Application flow of the Go tool.}
  \end{figure}

\subsection{Summary and Description}

A correlational analysis revealed a weak positive/negative (one of them, depending on context) relationship
with \emph{r} = \dots, \emph{p} = \dots.

\begin{figure}
  \begin{center}
  \includegraphics[scale=0.25]{images/fields_complexity.png}
  \end{center}
  \caption{\label{fields}Application flow of the Go tool.}
  \end{figure}

\subsection{Grammar Correctness}

A correlational analysis revealed a weak positive/negative (one of them, depending on context) relationship
with \emph{r} = \dots, \emph{p} = \dots.

\begin{figure}
  \begin{center}
  \includegraphics[scale=0.25]{images/grammar_correctness.png}
  \end{center}
  \caption{\label{grammar}Application flow of the Go tool.}
  \end{figure}

\subsection{Sentiment Scores}

A correlational analysis revealed a weak positive/negative (one of them, depending on context) relationship
with \emph{r} = \dots, \emph{p} = \dots.

\begin{figure}
  \begin{center}
  \includegraphics[scale=0.25]{images/sentiment_analysis.png}
  \end{center}
  \caption{\label{sentiment}Application flow of the Go tool.}
  \end{figure}
